title: "hw5_CA_MCA"
author: "Olga Zueva"

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ca)
library(dplyr)
library(ggplot2)
library(ggfortify)

##5.1
```{r}

data <- read.csv("https://raw.githubusercontent.com/agricolamz/2019_data_analysis_for_linguists/master/data/students/OlgaZueva98/hw5_CA_MCA/hw5_chairs.csv")
myvars <- names(data) %in% c("Shop", "WordDE", "Category")
newdata <- data[!myvars]
MCA <- MASS::mca(newdata)
data <- cbind(data, MCA$rs)
variables <- as_data_frame(MCA$cs)
variables$var_names <- rownames(MCA$cs)
data %>% 
  ggplot(aes(`1`, `2`))+
  geom_point(aes(color = Category))+
  stat_ellipse(aes(color = Category))+
  geom_text(data = variables, aes(`1`, `2`, label = var_names))+
  theme_bw()+
  scale_x_continuous(limits = c(-0.015, 0.02))

##5.3
```{r}

data_2 <- read.csv('https://raw.githubusercontent.com/agricolamz/2019_data_analysis_for_linguists/master/data/students/OlgaZueva98/hw5_CA_MCA/hw5_colreg.csv')
rownames(data_2) <- data_2$colors
ca <- ca(data_2[, -5])
data_2_col <- data.frame(ca$colcoord)
data_2_col$rows <- rownames(ca$colcoord)

data_2_row <- data.frame(ca$rowcoord)
data_2_row$rows <- rownames(ca$rowcoord)

data_2_col %>% 
  ggplot(aes(Dim1, Dim2, label = rows))+
  geom_text(color = "darkblue")+
  geom_text(data = data_2_row, color = "red")+
  theme_bw()+
  labs(x = "Dim1 (42.1%)",
       y = "Dim2 (32.6%)")

PCA <- prcomp(data_2[, -5])
autoplot(PCA,
         shape = FALSE,
         loadings = TRUE,
         label = TRUE,
         loadings.label = TRUE)
